---
title: "hong cao biostat 620 hw1"
output: html_notebook
---


```{r}
data= read.csv("screentime.csv",header = T)
head(data,5)
```
problem 1
(a)
We aim at studying individual behaviors using mobile devices such as smartphone, pads and wearable computer that measures screen use activities. 
my hypothesis is the total social media time has a relationship with the people's outdoor time.
reference : When the findings are analyzed, it has been found out that social media encourages travel, creates intercultural interactions and alternative leisure, incents leisure activities and facilitates making use of leisure. 
AYDIN B, Arslan E. The role of social media on leisure preferences: A research on the participants of outdoor recreation activities[J]. Turizm Akademik Dergisi, 2016, 3(1): 1-10.


(b)let participants know the purpose of study ,researcher of study, the risk and other information.
tell particapants what they will do.

(c) the data is collected from 12/31/2023-26/1/2024, total of 27 rows of data. included total screen time, total media tiem , daily pick times the first pick time(start form 5 am) and total video time(defime as the total time that the person watch vedio on this device).the data was all collected from the user's smartphones.
(d)  add the variable in the excel.

problem 2
```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
library(lubridate)
library(readr)
```
a
```{r}
data$Date <- mdy(data$Date)

data_long <- data %>%
  select(Date, Total.ST.min, Social.ST.min, Pickups, proportion.Social.ST, useduration) %>%
  pivot_longer(cols = -Date, names_to = "variable", values_to = "value")

# Plot time series for each variable
ggplot(data_long, aes(x = Date, y = value)) +
  geom_line() +
  facet_wrap(~variable, scales = "free_y", ncol = 1) +
  theme_minimal() +
  labs(x = "Date", y = "Value", title = "Time Series Plot of Screen Activity Variables")

```
there is a drop in the first week and keep constant in the following 2 weeks the there is another dorp.

b
```{r}
library(readr)
library(GGally)
pairwise_plot <- ggpairs(data, columns = c("Total.ST.min", "Social.ST.min", "Pickups", "proportion.Social.ST", "useduration"))

print(pairwise_plot)


```
pick up times and use duration have the 
highest corr.

(c)
```{r}

data <- data %>%
  mutate(cumulative_total_screen_time = cumsum(Total.ST.min),
         cumulative_social_screen_time = cumsum(Social.ST.min),
         cumulative_pickups = cumsum(Pickups),
         cumulative_proportion_social_screen_time = cumsum(proportion.Social.ST),
         cumulative_duration_per_use = cumsum(useduration))


plot(data$cumulative_total_screen_time, type = 'l', col = 'blue', xlab = "Observation", ylab = "Cumulative Time", main = "Occupation Time Curve")
lines(data$cumulative_social_screen_time, col = 'red')
lines(data$cumulative_pickups, col = 'green')
lines(data$cumulative_proportion_social_screen_time, col = 'purple')
lines(data$cumulative_duration_per_use, col = 'orange')


```
(d)
```{r}
library(stats)
variables <- c("Total.ST.min", "Social.ST.min", "Pickups", "proportion.Social.ST", "useduration")

acf_results <- list()

for (var in variables) {
  acf_results[[var]] <- acf(data[[var]], plot = T)
  print(paste("ACF for", var))
  print(acf_results[[var]])
}


```
Total.ST.min,Social.ST.min,useduration have significant autocorrelations at lag 1



problem3
```{r}
library(circular)
time_to_degrees <- function(time) {
  parts <- strsplit(time, ":")[[1]]
  hour <- as.numeric(parts[1])
  minute <- as.numeric(parts[2])
  # Convert time to fraction of 24-hour day
  time_fraction <- hour / 24 + minute / (24 * 60)
  # Convert fraction of day to degrees
  degrees <- time_fraction * 360
  return(degrees)
}

data$first_pickup_degrees <- sapply(data$Pickup.1st.start.from.5.00, time_to_degrees)

data_circular <- circular(data$first_pickup_degrees, units = "degrees", template = "clock24")
plot(data_circular)



```
```{r}
plot(data_circular, stack=TRUE, bins=360/2.5) 
```


problem 4
a
st is a factor to adjust the expected number of pickups according to the daily screen time, making the model more accurate for days with varying amounts of screen time.
b
```{r}
library(stats)
model <- glm(Pickups ~ offset(log(Total.ST.min)), 
                     family = poisson(link = "log"), data = data)

# Print the summary of the model to see the estimated coefficients
summary(model)

```
```{r}

loglinermodel <- glm(Pickups  ~ Xt + Zt, 
                     family = poisson(link = "log"), data = data)

summary_loglinermodel <- summary(loglinermodel)
print(summary_loglinermodel)



```
the H0 is both Xt0=Xt1 and Zt0=Zt1, the p value is both<0.05 is significant take H1, so the behavior is different in weedkdays,weekends  and different in vacation and new semester.

problem 5
```{r}

data$first_pickup_degrees <- sapply(data$Pickup.1st.start.from.5.00, time_to_degrees)
data_circular <- circular(data$first_pickup_degrees, units = "degrees", template = "clock24")

vonmises_fit <- mle.vonmises(data_circular)

print(vonmises_fit)

```


```{r}
angle_830AM <- (time_to_degrees("08:30") * 2 * pi)/360- pi
angle_830AM_circular <- circular(angle_830AM, type = 'angles', units = 'radians')
cdf <- pvonmises(angle_830AM_circular, vonmises_fit$mu, vonmises_fit$kappa)

# The probability that the first pickup is at 8:30 AM or later
probability <- 1 - cdf
probability
```


