---
title: "R Notebook"
output: html_notebook
---
hong cao
 biostat hw2 code


```{r}
library(systemfit)
library(dplyr)
data= read.csv("screentime.csv",header = T)
head(data,5)
```
a
```{r}
Y1_lag1 <- c(NA, data$Total.ST.min[-nrow(data)])
Y2_lag1 <- c(NA, data$Social.ST.min[-nrow(data)])
```

```{r}
sur_model1 <- systemfit(Total.ST.min ~ Y1_lag1 + Xt + Zt, "SUR", data = data)
summary(sur_model1)
```
in model 1, only the p value of intercept is < 0.05 is significant,suggesting that the average value of the response variable is significantly different from zero. the other term is not significant means that they are not have a significant effect on total screen time.
```{r}
sur_model2 <- systemfit(Social.ST.min ~ Y2_lag1 + Xt + Zt, "SUR", data = data)
summary(sur_model2)
```
b
in model 1, only the p value of intercept is < 0.05 is significant,suggesting that the average value of the response variable is significantly different from zero. the other term is not significant means that they are not have a significant effect on total screen time.

in model 2 except intercept the Y2_lag1 p value is significant （0.0242388） ,< 0.05 means it have significant effect on total social screen time


```{r}
C_matrix <- matrix(c(0, 0, 0, 1), nrow = 1, byrow = TRUE)
vcov_matrix <- vcov(sur_model1)
wald_stat <- t(C_matrix %*% coef(sur_model1)) %*% solve(C_matrix %*% vcov_matrix %*% t(C_matrix)) %*% (C_matrix %*% coef(sur_model1))
df <- nrow(C_matrix)
p_value <- 1 - pchisq(wald_stat, df)
p_value
```
```{r}
C_matrix <- matrix(c(0, 0, 0, 1), nrow = 1, byrow = TRUE)
vcov_matrix <- vcov(sur_model2)
wald_stat <- t(C_matrix %*% coef(sur_model2)) %*% solve(C_matrix %*% vcov_matrix %*% t(C_matrix)) %*% (C_matrix %*% coef(sur_model2))
df <- nrow(C_matrix)
p_value <- 1 - pchisq(wald_stat, df)
p_value
```
both model's hypothesis test for Zt shows that the p value is large than 0.05 which means we can not reject H0,Zt is not a significant predictor.



4d
```{r}
data = [(Z1, X1, Y1) to  (Zn, Xn, Yn)]
num_bootstraps = 1000
bootstrap_estimates = []

for i in 1 to num_bootstraps do:
    bootstrap_sample = sample_with_replacement(original_data, size=n)
    # CACULATE alpha_hat
    # CACULATE beta_hat
    beta_iv_star = beta_hat / alpha_hat
    append(bootstrap_estimates, beta_iv_star)

variance_beta_iv = variance(bootstrap_estimates)

```
