---
output:
  html_document: default
  pdf_document: default
  word_document: default
---
problem1 is in another document

problen2
a
```{r}
A <- c(1, 1, 1, 1, 0, 0, 0, 0,0)
mrate <- c(11, 14, 24, 20, 26, 20, 3, 7,8)
hcover <- c(0.06, 0.07, 0.06, 0.07, 0.07, 0.06, 0.02, 0.02, 0.01)
pcdocs <- c(0.02, 0.01, 0.02, 0.01, 0.02, 0.01, 0.04, 0.04, 0.05)
data=cbind(A, mrate, hcover, pcdocs)
mydata=data.frame(data)
psmodel <- glm(A ~ hcover + pcdocs, family=binomial, data = mydata)
summary(psmodel)
pscore <- round(psmodel$fitted,3)
print(pscore)
```


```{r}
pscorematch <- function(data,A) {
  df <- cbind(data, pscore)
  match <- list()
  controls <- which(A == 0)
  
  for (i in which(A == 1)) {
    ps_diff <- abs(pscore[i] - df$pscore[controls])
    greed <- controls[which.min(ps_diff)]
    match[[i]] <- c(i, greed)
    controls <- which(A == 0) 
    controls <- controls[-which(controls == greed)]
  }
  return(list(Match.pairs = match, Propensity = pscore))
}
result1 = pscorematch(data = mydata, A = mydata$A)
print(result1$Match.pairs)
print(result1$Propensity)
```
b
```{r}
  treatment <- mydata$mrate[unlist(sapply(result1$Match.pairs, function(x) x[1]))]
  control <- mydata$mrate[unlist(sapply(result1$Match.pairs, function(x) x[2]))]
  ate <- mean(treatment) - mean(control)
  n <- length(result1$Match.pairs)
  n_treatment <- length(treatment)
  n_control <- length(control)
  sd <- sqrt(var(treatment) / n_treatment + var(control) / n_control)
  standard_error <- sd / sqrt(n)
  t_stat <- ate / standard_error
  df <- n - 1
  p_value <- 2 * pt(-abs(t_stat), df)
  print(ate)
  print(sd)
  print(p_value)
```
c
```{r}
pscore = psmodel$fitted
A = mydata[,1]

# Computing propensity scores for both groups
pscore1 = pscore[A==1]
pscore0 = pscore[A==0]

# Generating histograms for both groups
hpscore1 = hist(pscore1)
hpscore0 = hist(pscore0)

# Making the counts of the second histogram negative
hpscore0$counts = -hpscore0$counts

# Plotting the histogram for the first group
plot(hpscore1, xlab="propensity scores", xlim=c(0.1,0.9), ylim=c(-1,1),
     col="red", main="Histograms of propensity scores")

# Adding the histogram for the second group to the plot
lines(hpscore0, col="blue")
```
```{r}
library(Matching)
library(MatchIt)
match.out= matchit(A ~ hcover+pcdocs,data=mydata, method="nearest")
summary(match.out)
plot(match.out, type="jitter")
plot(match.out, type="hist")
```
```{r}
numerator <- abs(mean(treatment) - mean(control))
denominator <- sqrt((sd(treatment)^2 + sd(control)^2)/2)
smd <- numerator/denominator
smd
```
d merge them together
```{r}
pscorematch <- function(data,A) {
  df <- cbind(data, pscore)
  match <- list()
  controls <- which(A == 0)
  
  for (i in which(A == 1)) {
    ps_diff <- abs(pscore[i] - df$pscore[controls])
    greed <- controls[which.min(ps_diff)]
    match[[i]] <- c(i, greed)
    controls <- which(A == 0) 
    controls <- controls[-which(controls == greed)]
  }
  return(list(Match.pairs = match, Propensity = pscore))
}
result1 = pscorematch(data = mydata, A = mydata$A)
print(result1$Match.pairs)
print(result1$Propensity)
 treatment <- mydata$mrate[unlist(sapply(result1$Match.pairs, function(x) x[1]))]
  control <- mydata$mrate[unlist(sapply(result1$Match.pairs, function(x) x[2]))]
  ate <- mean(treatment) - mean(control)
  n <- length(result1$Match.pairs)
  n_treatment <- length(treatment)
  n_control <- length(control)
  sd <- sqrt(var(treatment) / n_treatment + var(control) / n_control)
  standard_error <- sd / sqrt(n)
  t_stat <- ate / standard_error
  df <- n - 1
  p_value <- 2 * pt(-abs(t_stat), df)
  print(ate)
  print(sd)
  print(p_value)
  pscore = psmodel$fitted
A = mydata[,1]

# Computing propensity scores for both groups
pscore1 = pscore[A==1]
pscore0 = pscore[A==0]

# Generating histograms for both groups
hpscore1 = hist(pscore1)
hpscore0 = hist(pscore0)

# Making the counts of the second histogram negative
hpscore0$counts = -hpscore0$counts

# Plotting the histogram for the first group
plot(hpscore1, xlab="propensity scores", xlim=c(0.1,0.9), ylim=c(-1,1),
     col="red", main="Histograms of propensity scores")

# Adding the histogram for the second group to the plot
lines(hpscore0, col="blue")
numerator <- abs(mean(treatment) - mean(control))
denominator <- sqrt((sd(treatment)^2 + sd(control)^2)/2)
smd <- numerator/denominator
smd
```

problem3
```{r,warning=FALSE}
library(readxl)
library(ggplot2)
library(dplyr)
library(Matching)
library(boot)
screentime <- read_excel("ScreenTime-hw3Q3.xlsx", sheet="ScreenTime")
baseline <- read_excel("ScreenTime-hw3Q3.xlsx", sheet="Baseline")
mydata2 <- merge(screentime, baseline, by="pseudo_id")

```

```{r}
mydata2_ap <-mydata2[mydata2$Treatment != "B",]
mydata2_bp <-mydata2[mydata2$Treatment != "A",]
mydata2_ap$Treatment <- ifelse(mydata2_ap$Treatment == "A", 1, 0)
mydata2_bp$Treatment <- ifelse(mydata2_bp$Treatment == "B", 1, 0)

```
a
ap
```{r}
ap_model <- glm(Treatment ~ sex + age + pets + siblings, family=binomial(), data=mydata2_ap)
pscore_ap <- round(ap_model$fitted,3)
pscorematch_ap <- function(data,A) {
  df <- cbind(data, pscore_ap)
  match <- list()
  controls <- which(A == 0)
  
  for (i in which(A == 1)) {
    ps_diff <- abs(pscore_ap[i] - df$pscore_ap[controls])
    greed <- controls[which.min(ps_diff)]
    match[[i]] <- c(i, greed)
    controls <- which(A == 0) 
    controls <- controls[-which(controls == greed)]
  }
  return(list(Match.pairs = match, Propensity = pscore_ap))
}

result2 = pscorematch_ap(data = mydata2_ap, A = mydata2_ap$Treatment)
print(result2$Match.pairs)
print(result2$Propensity)
reatment <- mydata2_bp$Treatment[unlist(sapply(result2$Match.pairs, function(x) x[1]))]
control <- mydata2_bp$Treatment[unlist(sapply(result2$Match.pairs, function(x) x[2]))]
numerator <- abs(mean(treatment) - mean(control))
denominator <- sqrt((sd(treatment)^2 + sd(control)^2)/2)
smd <- numerator/denominator
smd
```
a 
bp
```{r}
bp_model <- glm(Treatment ~ sex + age + pets + siblings, family=binomial(), data=mydata2_bp)
pscore_bp <- round(bp_model$fitted,3)
pscorematch_bp <- function(data,A) {
  df <- cbind(data, pscore_bp)
  match <- list()
  controls <- which(A == 0)
  
  for (i in which(A == 1)) {
    ps_diff <- abs(pscore_bp[i] - df$pscore_bp[controls])
    greed <- controls[which.min(ps_diff)]
    match[[i]] <- c(i, greed)
    controls <- which(A == 0) 
    controls <- controls[-which(controls == greed)]
  }
  return(list(Match.pairs = match, Propensity = pscore_bp))
}
result3 = pscorematch_bp(data = mydata2_bp, A = mydata2_bp$Treatment)
print(result3$Match.pairs)
print(result3$Propensity)
reatment <- mydata2_bp$Treatment[unlist(sapply(result3$Match.pairs, function(x) x[1]))]
control <- mydata2_bp$Treatment[unlist(sapply(result3$Match.pairs, function(x) x[2]))]
numerator <- abs(mean(treatment) - mean(control))
denominator <- sqrt((sd(treatment)^2 + sd(control)^2)/2)
smd <- numerator/denominator
smd
```
b
ap
```{r}
  treatment <- mydata2_ap$Tot.Soc.Time[unlist(sapply(result2$Match.pairs, function(x) x[1]))]
  control <- mydata2_ap$Tot.Soc.Time[unlist(sapply(result2$Match.pairs, function(x) x[2]))]
  ate <- mean(treatment) - mean(control)
  n <- length(result1$Match.pairs)
  n_treatment <- length(treatment)
  n_control <- length(control)
  sd <- sqrt(var(treatment) / n_treatment + var(control) / n_control)
  standard_error <- sd / sqrt(n)
  t_stat <- ate / standard_error
  df <- n - 1
  p_value <- 2 * pt(-abs(t_stat), df)
  print(ate)
  print(sd)
  print(p_value)

```
h0= a and p have no difference.h1 a and p have difference p < 0.05 reject h0 . intervention A (persuasion) have effective to reduce the daily total
social screen time in comparison to the placebo P

b
bp
```{r}
treatment <- mydata2_bp$Tot.Soc.Time[unlist(sapply(result2$Match.pairs, function(x) x[1]))]
control <- mydata2_bp$Tot.Soc.Time[unlist(sapply(result2$Match.pairs, function(x) x[2]))]
  ate <- mean(treatment) - mean(control)
  n <- length(result1$Match.pairs)
  n_treatment <- length(treatment)
  n_control <- length(control)
  sd <- sqrt(var(treatment) / n_treatment + var(control) / n_control)
  standard_error <- sd / sqrt(n)
  t_stat <- ate / standard_error
  df <- n - 1
  p_value <- 2 * pt(-abs(t_stat), df)
  print(ate)
  print(sd)
  print(p_value)
```
h0= b and p have no difference.h1 b and p have difference p < 0.05 reject h0 . intervention B (competition) have effective to reduce the daily total
social screen time in comparison to the placebo P

c
```{r}
library(tableone)
formula <- Treatment ~ sex + age + pets + siblings
prop_ap_model <- glm(formula, family=binomial(), data=mydata2_ap)
prop_ap_fitted <- prop_ap_model$fitted
repeat_ap <- Match(Tr=mydata2_ap$Treatment, M=1, X=logit(pscore_ap), replace=FALSE, caliper=0.1)
matched_ap <- mydata2_ap[unlist(repeat_ap[c("index.treated","index.control")]),]
var <- c("Tot.Soc.Time")
matched_tab_ap <- CreateTableOne(vars=var, strata="Treatment", data=matched_ap, test=TRUE)
print(matched_tab_ap, smd=TRUE)

prop_bp_model <- glm(formula, family=binomial(), data=mydata2_bp)
prop_bp_fitted <- prop_bp_model$fitted
repeat_bp <- Match(Tr=mydata2_bp$Treatment, M=1, X=logit(prop_bp_fitted), replace=FALSE, caliper=0.1)
matched_out_bp <- mydata2_bp[unlist(repeat_bp[c("index.treated","index.control")]),]
var <- c("Tot.Soc.Time")
matched_tab_bp <- CreateTableOne(vars=var, strata="Treatment", data=matched_out_bp, test=TRUE)
print(matched_tab_bp, smd=TRUE)
```




problem 4
```{r}
merge_sub <- mydata2[mydata2$Treatment != "P",]
merge_sub$Treatment <- ifelse(merge_sub$Treatment == "A", 1, 0)

regression_model <- lm(Tot.Soc.Time ~ Treatment + sex + age + pets + siblings, data=merge_sub)
summary(regression_model)

```
pvalue of treatment< 0.05 is sinificant,the adjusted differential treatment effect statistically significant

b
```{r}
ipw_model <- glm(Treatment ~ sex + age + pets + siblings,
                 family=binomial(link="logit"), data=merge_sub)
propens <- ipw_model$fitted
w <- 1/propens
wbar <- 1/(1-propens)
ipw_diff_treat <- sum(w*merge_sub$Treatment*merge_sub$Tot.Soc.Time)/sum(w*merge_sub$Treatment) -
  sum(wbar*(1-merge_sub$Treatment)*merge_sub$Tot.Soc.Time)/sum(wbar*(1-merge_sub$Treatment))
print(ipw_diff_treat)
```
c
Multiple Regression Analysis: Assumes that the model correctly specifies therelationship between the outcome and both the treatment and covariates.
IPW Method: Relies on the correct specification of the propensity score model ratherthan the outcome model.
Using the IPW method, the di!erential treatment e!ect is ≠85.90145, meaning that a person with an addition
of treatment enjoys a reduced total social screen time by 86 minutes.
