---
title: " caohong biostat hw4 "
output: html_notebook
---

hong cao
biostat hw4 code
GITHUB LINK https://github.com/nxdlll/620-hw

```{r}
library(readxl)
library(dplyr)
library(purrr)
screentime <- read_excel("ScreenTime-hw3Q3.xlsx", sheet="ScreenTime")
baseline <- read_excel("ScreenTime-hw3Q3.xlsx", sheet="Baseline")
data <- merge(screentime, baseline, by="pseudo_id")
head(data)

```
a
```{r}
# focus on B
dataB = data[data$Treatment == "B",]
dataB$X = ifelse(dataB$Day == "Su" | dataB$Day == "Sa", 0, 1 )
dataB$B = ifelse(dataB$Phase == "Baseline",  0, 1)
head(dataB)
```
```{r}
dataB$lagged_y = lag(dataB$Pickups, n = 1, default = NA)
```

```{r}
id2 = dataB[dataB$pseudo_id == 2,]
model2 = glm(Pickups ~ lagged_y + B + X, data = id2, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(model2)
```
```{r}
id3 = dataB[dataB$pseudo_id == 3,]
model3 = glm(Pickups ~ lagged_y + B + X, data = id3, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(model3)
```
```{r}
id4 = dataB[dataB$pseudo_id == 4,]
model4 = glm(Pickups ~ lagged_y + B + X, data = id4, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(model4)
```
```{r}
id5= dataB[dataB$pseudo_id == 5,]
model5 = glm(Pickups ~ lagged_y + B + X, data = id5, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(model5)
```
```{r}
id8 = dataB[dataB$pseudo_id == 8,]
model8 = glm(Pickups ~ lagged_y + B + X, data = id8, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(model8)
```
```{r}
id15 = dataB[dataB$pseudo_id == 15,]
model15 = glm(Pickups ~ lagged_y + B + X, data = id15, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(model15)
```
```{r}
id16 = dataB[dataB$pseudo_id == 16,]
model16= glm(Pickups ~ lagged_y + B + X, data = id16, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(model16)
```

```{r}
id18 = dataB[dataB$pseudo_id ==18,]
model18 = glm(Pickups ~ lagged_y + B + X, data = id18, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(model18)
```
b
$$
\mathrm{Var}(\hat{\beta}_{\text{meta}, j}) = \frac{1}{\frac{1}{\mathrm{Var}(\hat{\beta}_{1,j})} + \dots + \frac{1}{\mathrm{Var}(\hat{\beta}_{k,j})}}
$$
```{r}
meta_estimates0 = 1/(1/(summary(model2)$coefficients[, "Std. Error"][1])^2 + 1/(summary(model3)$coefficients[, "Std. Error"][1])^2
               + 1/(summary(model4)$coefficients[, "Std. Error"][1])^2 + 1/(summary(model5)$coefficients[, "Std. Error"][1])^2
               + 1/(summary(model8)$coefficients[, "Std. Error"][1])^2 +  1/(summary(model15)$coefficients[, "Std. Error"][1])^2
               + 1/(summary(model16)$coefficients[, "Std. Error"][1])^2)
meta_estimates0
```

```{r}
meta_estimates1 =1/(1/(summary(model2)$coefficients[, "Std. Error"][2])^2 + 1/(summary(model3)$coefficients[, "Std. Error"][2])^2
               + 1/(summary(model4)$coefficients[, "Std. Error"][2])^2 + 1/(summary(model5)$coefficients[, "Std. Error"][2])^2
               + 1/(summary(model8)$coefficients[, "Std. Error"][2])^2 +  1/(summary(model15)$coefficients[, "Std. Error"][2])^2
               + 1/(summary(model16)$coefficients[, "Std. Error"][2])^2 )
meta_estimates1
```
```{r}
meta_estimates2=1/(1/(summary(model2)$coefficients[, "Std. Error"][3])^2 + 1/(summary(model3)$coefficients[, "Std. Error"][3])^2
               + 1/(summary(model4)$coefficients[, "Std. Error"][3])^2 + 1/(summary(model5)$coefficients[, "Std. Error"][3])^2
               + 1/(summary(model8)$coefficients[, "Std. Error"][3])^2 +  1/(summary(model15)$coefficients[, "Std. Error"][3])^2
               + 1/(summary(model16)$coefficients[, "Std. Error"][3])^2 )


meta_estimates2
```

```{r}
meta_estimates3=1/(1/(summary(model2)$coefficients[, "Std. Error"][4])^2 + 1/(summary(model3)$coefficients[, "Std. Error"][4])^2
               + 1/(summary(model4)$coefficients[, "Std. Error"][4])^2 + 1/(summary(model5)$coefficients[, "Std. Error"][4])^2
               + 1/(summary(model8)$coefficients[, "Std. Error"][4])^2 +  1/(summary(model15)$coefficients[, "Std. Error"][4])^2
               + 1/(summary(model16)$coefficients[, "Std. Error"][4])^2 )


meta_estimates3

```
c
```{r}
modelall= glm(Pickups ~ lagged_y + B + X, data = dataB, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(modelall)
```
$$
H_{0}:\beta_2 \ne 0  \ \ H_{1}:\beta_2 = 0
$$
pvalue is  <2e-16 *** is significant reject h0 take h1. intervention B (competition) effective to reduce the daily number of pickups in comparison to
the no intervention at the baseline 

d

Federated Learning Lacks Flexibility
Federated Learning may be Communication Expensive
Summary statistics to be shared are always the same types, regardless
of statistical problems: point estimate and its variance (or std err).
Meta learning assumes (i) independent samples from different study
sites ; (ii) homogeneous target model parameters across study sites,
which may be violated
In the literature, oftentimes local model specifications allow to be
different, which should not be taken for granted for the sake of
interpretability.


problem3 
a
```{r}
dataA = data[data$Treatment != "P" ,]
dataA$X <- ifelse(dataA$Day == "Su" | dataA$Day == "Sa", 0, 1 )
dataA$B <- ifelse(dataA$Phase == "Baseline",  0, 1)
dataA$lagged_y = lag(dataA$Pickups, n = 1, default = NA)
head(dataA)
```
```{r}
pA = dataA[dataA$Treatment == "A",]
pB = dataA[dataA$Treatment == "B",]
```

```{r}
M1 = glm(Pickups ~ lagged_y + B + X +sex + age + pets + siblings, data = pA, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(M1)
```
```{r}
M2 = glm(Pickups ~ lagged_y + B + X +sex + age + pets + siblings, data = pB, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(M2)
```
```{r}
meta_estimates_Intercept=1/(1/(summary(M1)$coefficients[, "Std. Error"][1])^2 + 1/(summary(M2)$coefficients[, "Std. Error"][1])^2)
meta_estimatesIntercept
```
```{r}
meta_estimates_lagged_y =1/(1/(summary(M1)$coefficients[, "Std. Error"][2])^2 + 1/(summary(M2)$coefficients[, "Std. Error"][2])^2)
meta_estimates_lagged_y
```
```{r}
meta_estimates_B =1/(1/(summary(M1)$coefficients[, "Std. Error"][3])^2 + 1/(summary(M2)$coefficients[, "Std. Error"][3])^2)
meta_estimates_B
```
```{r}
meta_estimates_X =1/(1/(summary(M1)$coefficients[, "Std. Error"][4])^2 + 1/(summary(M2)$coefficients[, "Std. Error"][4])^2)
meta_estimates_X
```
```{r}
meta_estimates_sex =1/(1/(summary(M1)$coefficients[, "Std. Error"][5])^2 + 1/(summary(M2)$coefficients[, "Std. Error"][5])^2)
meta_estimates_sex
```
```{r}
meta_estimates_age =1/(1/(summary(M1)$coefficients[, "Std. Error"][6])^2 + 1/(summary(M2)$coefficients[, "Std. Error"][6])^2)
meta_estimates_age
```
```{r}
meta_estimates_pets =1/(1/(summary(M1)$coefficients[, "Std. Error"][7])^2 + 1/(summary(M2)$coefficients[, "Std. Error"][7])^2)
meta_estimates_pets
```

```{r}
meta_estimates_sibilings =1/(1/(summary(M1)$coefficients[, "Std. Error"][8])^2 + 1/(summary(M2)$coefficients[, "Std. Error"][8])^2)
meta_estimates_sibilings
```
b
in both model pvalue of B is < 0.05 is significant ,intervention reduced daily number of pickups

c
```{r}
M3 = glm(Pickups ~ lagged_y + B + X +sex + age + pets + siblings, data = dataA, family = poisson(link = "log"), offset = log(Tot.Scr.Time))
summary(M3)
```
 pvalue of B is < 0.05 is significant ,intervention reduced daily number of pickups
 
 d
 for part b, we need to build a GLM for intervention A and intervention B separately then combined A and B to perform meta learning.for partc, we do not need to calculate intervention A and B separately
